### 2020-07-31 manuscript.tex
tidy ups

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/tournament.pdf}
\caption{\textbf{Protocol for optimising methodology settings.} The three areas (detailed in \textbf{\nameref{sect:models}}) are optimised sequentially, where the best setting from each step is used when optimising the following step.}
\label{fig:tournament}
\end{figure}

>>>>

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/tournament.pdf}
\caption{\textbf{Protocol for optimising clock model methodologies.} Each area (detailed in \textbf{\nameref{sect:models}}) is optimised sequentially, and the best setting from each step is used when optimising the following step.}
\label{fig:tournament}
\end{figure}
